%-------------------------
% Academic CV — Abu Jafar Saifullah
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{{#1 \vspace{-2pt}}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeEducationHeading}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
\begin{document}

%---------- HEADING ----------

\begin{center}
    \textbf{\Huge \scshape Abu Jafar Saifullah} \\ \vspace{3pt}
    \small
    \faMobile \hspace{.5pt} \href{tel:+8801717743519}{+880 1717 743519}
    $|$
    \faAt \hspace{.5pt} \href{mailto:jafarmahin107@gmail.com}{jafarmahin107@gmail.com}
    $|$
    \faLinkedinSquare \hspace{.5pt} \href{https://www.linkedin.com/in/abu-jafar-saifullah/}{LinkedIn}
    $|$
    \faGithub \hspace{.5pt} \href{https://github.com/jaf107}{GitHub}
    $|$
    \faMapMarker \hspace{.5pt} {Dhaka, Bangladesh}
\end{center}


%----------- RESEARCH INTERESTS -----------

\section{Research Interests}
  \vspace{3pt}
  \resumeSubHeadingListStart
    \small{\item{
      Web Accessibility, Automated Program Repair, Software Testing, Dynamic Analysis, NLP for Software Engineering
    }}
  \resumeSubHeadingListEnd


%----------- EDUCATION -----------

\section{Education}
  \vspace{3pt}
  \resumeSubHeadingListStart

    \resumeEducationHeading
      {University of Dhaka}{Dhaka, Bangladesh}
      {M.Sc. in Software Engineering (Final Semester); \textbf{GPA: 3.92/4.00}}{Apr 2025 \textbf{--} Aug 2026}
      {B.Sc. in Software Engineering; \textbf{GPA: 3.89/4.00}}{Jan 2019 \textbf{--} Dec 2023}

    \resumeSubheading
      {Notre Dame College}{Dhaka, Bangladesh}
      {Higher Secondary Certificate; \textbf{GPA: 5.0/5.0}}{Jun 2014 \textbf{--} Jun 2016}

  \resumeSubHeadingListEnd


%----------- PUBLICATIONS -----------

\section{Publications}
  \vspace{3pt}
  \resumeSubHeadingListStart
    \small{\item{
      \textbf{Abu Jafar Saifullah}, Tasmia Zerin, Zerina Begum, Kazi Sakib. \textit{``NavA11y: A Dynamic Analysis Approach for WCAG 2.4 Focus-Behavior Evaluation.''} In \textit{Proceedings of the International Conference on Evaluation of Novel Approaches to Software Engineering} \textbf{(ENASE 2026)}. \textit{Accepted.} \hfill \href{https://anonymous.4open.science/r/NavA11y-2C9E}{\color{blue}[Code]}
      \vspace{4pt}

      \textit{Key results:} 100\% precision and recall on a 22-page controlled dataset (32 SC-level assertions); 2,947 violations detected across 26 production websites; 90\% precision confirmed via independent manual validation (PABAK = 0.80). First tool to cover all five WCAG 2.4 focus-behavior success criteria.
    }}
  \resumeSubHeadingListEnd


%----------- RESEARCH EXPERIENCE -----------

\section{Research Experience}
  \vspace{3pt}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Institute of Information Technology, University of Dhaka}{Dhaka, Bangladesh}
      {Graduate Researcher, supervised by \href{https://iit.du.ac.bd/faculty/profile/sakib}{\color{blue}Dr. Kazi Sakib} \& Zerina Begum}{Apr 2025 \textbf{--} Present}
        \resumeItemListStart
            \resumeItem{Developing \textbf{NavA11y}, a dynamic analysis tool for automated WCAG 2.4 accessibility evaluation using Playwright-driven browser automation. Research forms the core of M.Sc. thesis.}
            \resumeItem{Designed a two-phase analysis architecture: Page-Level Analysis (keyboard traversal, Kendall $\tau$ divergence scoring) and Element-Level Analysis (focus-state inspection, 7$\times$7 grid obscuration probing).}
            \resumeItem{Constructed and released a 22-page labeled focus-behavior dataset (\textit{Dd}) covering all five WCAG 2.4 focus-behavior SCs, including pass, boundary, and obscuration cases.}
            \resumeItem{Conducted manual evaluation with two independent expert raters across 6 production websites; computed inter-rater agreement (PABAK = 0.80).}
        \resumeItemListEnd

    \resumeSubheading
      {SEMERU Lab, William \& Mary}{Remote}
      {Research Intern, supervised by \href{https://www.cs.wm.edu/~denys/}{\color{blue}Dr. Denys Poshyvanyk}}{Aug 2023 \textbf{--} Dec 2023}
        \resumeItemListStart
            \resumeItem{Built a programming language-specific tokenizer to improve NLP model predictions for software engineering tasks, contributing to the lab's research on intelligent software tools.}
        \resumeItemListEnd

  \resumeSubHeadingListEnd


%----------- INDUSTRY EXPERIENCE -----------

\section{Industry Experience}
  \vspace{3pt}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Optimizely, Content Marketing Platform}{Dhaka, Bangladesh}
      {Software Engineer II \textnormal{(promoted from SE I, Apr 2026)}}{Apr 2024 \textbf{--} Present, Full-time}
      \resumeItemListStart
        \resumeItem{Contributed to the platform's migration to \textbf{Axiom} (\href{https://github.com/optimizely-axiom/optiaxiom}{\color{blue}\texttt{@optiaxiom/react}}, public design system). Authored 15+ V1{\textrightarrow}V2 component conversions in the open-source repo and 10+ adapter components in the product. Wrote the Migration Guide and Icon Contribution Guide used by other product teams.}
        \resumeItem{Worked on end-to-end integration of an internal AI SDK. Migrated the backing service from Express to Hono, set up the AWS CodeArtifact publishing pipeline, and instrumented AI-context events across 10+ product surfaces.}
        \resumeItem{Implemented backend block-context extraction for LLM prompts, frontend block-form interaction, and AI resource rendering for the platform's AI document UI (Adaptive-Cards-style pattern).}
        \resumeItem{Implemented \textbf{Dark Mode} across 15+ surfaces (CSS-variable refactor) and contributed to \textbf{Spotlight} global search (built during, and won, the \textbf{Optimizely Global Hackathon 2025} as part of a team); reviewed \textbf{300+ pull requests} across design-system and AI-tracking work.}
      \resumeItemListEnd

    \resumeSubheading
      {Orion Informatics Ltd.}{Dhaka, Bangladesh}
      {Software Engineer}{Jul 2023 \textbf{--} Mar 2024, Full-time}
        \resumeItemListStart
            \resumeItem{Built data visualisation and reporting features for an Attendance Management System; developed a two-service ASP.NET Core webhook relay for TradeStation alerts deployed on Azure.}
        \resumeItemListEnd

  \resumeSubHeadingListEnd


%----------- RESEARCH PROJECTS -----------

\section{Research \& Academic Projects}
    \vspace{3pt}
    \resumeSubHeadingListStart

      \resumeProjectHeading
        {\textbf{NavA11y} $|$ \emph{Node.js, Playwright, Chromium, GitHub Actions} $|$ \href{https://anonymous.4open.science/r/NavA11y-2C9E}{\color{blue}Code} $|$ \textit{ENASE 2026}}{}
          \resumeItemListStart
            \resumeItem{Dynamic WCAG 2.4 accessibility testing tool, the first to cover all five focus-behavior SCs. Two-phase architecture: Page-Level Analysis (Kendall $\tau$ divergence scoring of tab traversal) and Element-Level Analysis (7$\times$7 grid obscuration probing, CSS focus-state inspection). 100\% precision/recall on 22-page labeled benchmark; 2,947 violations on 26 production sites; 90\% precision confirmed by independent expert raters (PABAK = 0.80). Dataset released for community benchmarking.}
          \resumeItemListEnd

      \resumeProjectHeading
        {\textbf{RepairA11y} $|$ \emph{Node.js, Playwright, Vitest} $|$ \textit{M.Sc. Thesis, In Progress, 2026}}{}
          \resumeItemListStart
            \resumeItem{LLM-driven accessibility repair pipeline evaluating whether runtime-evidence prompting (live DOM + NavA11y violation report) outperforms static-evidence prompting (HTML/screenshots) for automated WCAG 2.4 patch generation. Addresses four research questions covering effectiveness, evidence ablation, and regression safety.}
          \resumeItemListEnd

      \resumeProjectHeading
        {\textbf{Clippy} $|$ \emph{Angular, Node.js, AWS S3} $|$ \href{https://github.com/jaf107/Clippy}{\color{blue}GitHub} $|$ \textit{ICSE SRC 2023, Top 6}}{}
          \resumeItemListStart
            \resumeItem{Smart PDF reader with knowledge graph extraction, citation network visualization, and paper recommendation; submitted to ICSE 2023 Student Research Competition. 392 commits, 5 GitHub stars.}
          \resumeItemListEnd

      \resumeProjectHeading
        {\textbf{BPE Tokenizer} $|$ \emph{Python, Flask, HuggingFace} $|$ \href{https://pypi.org/project/python-bpe-tokenizer/}{\color{blue}PyPI}}{}
          \resumeItemListStart
            \resumeItem{Byte Pair Encoding tokenizer implemented from scratch and published as \texttt{python-bpe-tokenizer} on PyPI; includes a Flask web interface for training on custom corpora. Built as direct precursor to SEMERU Lab tokenizer research.}
          \resumeItemListEnd

      \resumeProjectHeading
        {\textbf{ML Bug Mining (SZZ)} $|$ \emph{Python, GitPython, pandas, scikit-learn} $|$ \textit{M.Sc. Coursework}}{}
          \resumeItemListStart
            \resumeItem{Mined ML-related bugs across 9 open-source repositories using the SZZ algorithm; identified bug-fixing and bug-introducing commits via keyword heuristics and git blame, filtered for ML-library-touching code.}
          \resumeItemListEnd

      \resumeProjectHeading
        {\textbf{Blueberry Auto} $|$ \emph{React, Hono, Supabase, Vercel} $|$ \href{https://blueberry.com.bd/}{\color{blue}Live} $|$ \textit{Lead Developer, 2025\,--\,Present}}{}
          \resumeItemListStart
            \resumeItem{Vehicle marketplace platform built as a pnpm monorepo (frontend, Hono API, Supabase backend, crawler); leading end-to-end build as the contracted developer.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd


%----------- SKILLS -----------

\section{Technical Skills}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{Languages:}{ TypeScript, JavaScript, Python, Java, C\#, C++} \\ \vspace{3pt}
        \textbf{Web \& Frontend:}{ React 18/19, Next.js, Angular, Node.js, Hono, Express, FastAPI, Spring Boot 3, ASP.NET Core} \\ \vspace{3pt}
        \textbf{Testing \& Automation:}{ Playwright, axe-core, Vitest, Karma, Mocha, Chai, Sinon, Selenium} \\ \vspace{3pt}
        \textbf{ML / NLP:}{ TensorFlow, HuggingFace Transformers, BPE Tokenization (own impl.), TextRank, TF-IDF, scikit-learn, pandas} \\ \vspace{3pt}
        \textbf{Research Methods:}{ Dynamic Program Analysis, Mining Software Repositories (SZZ), Controlled User Studies, Statistical Evaluation (Kendall $\tau$, Cohen's $\kappa$, PABAK), Inter-rater Agreement} \\ \vspace{3pt}
        \textbf{DevOps / Cloud:}{ AWS CodeArtifact, AWS S3, Azure, Cloudflare Workers, Docker, NGINX, GitHub Actions} \\ \vspace{3pt}
        \textbf{Databases:}{ MongoDB, PostgreSQL (Supabase), SQL Server, Firebase, Redis}
    }}
  \resumeSubHeadingListEnd


%----------- AWARDS & ACHIEVEMENTS -----------

\section{Awards \& Achievements}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{ICT Division Fellowship, Government of Bangladesh}: research funding for NavA11y / M.Sc. thesis (Grant No. 56.00.0000.052.33.002.24-61, Apr 2026) \\ \vspace{3pt}
        \textbf{Winner}, Optimizely Global Hackathon 2025 (company-wide international hackathon; team built Spotlight, shipped to CMP) \\ \vspace{3pt}
        \textbf{Top 6}, ICSE SCORE 2023 (international undergraduate SE competition) \\ \vspace{3pt}
        \textbf{Champion}, Refactoring Competition (2023) \hspace{10pt}
        \textbf{Best UI/UX}, Hackathon (2023) \\ \vspace{3pt}
        \textbf{Champion}, Project Showcasing (2022) \hspace{10pt}
        \textbf{Runners-up}, Project Showcasing (2021)
    }}
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
